Programming Distributed Control Planes

### 2016-01-21 paper/introduction.tex
tweaks to the leading paras

However, SDN does not help the vast majority of networks in the world, which  still operate a distributed control plane. For the foreseeable future, many of these networks will continue to operate a distributed control plane, due to the difficulty of migration or the challenges that centralized control planes face in terms of scaling and failure robustness. 
%, scaling challenges of centralized control, or the inherent robustness of distributed control planes to failures.
%It is difficult to scale centralized control planes both 
Centralized control planes need careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}.\footnote{For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.}

In this paper, we ask if it is possible to centrally program distributed control planes.
Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations. The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant even under failures.
If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes.

>>>>

Centralized control planes, however, are not a panacea. 
%They face significant challenges related to scaling and failure robustness. 
They require careful design and engineering to be robust to failures at scale---one must ensure that all devices can communicate with the controller at all times, even under arbitrary combinations of failure~\cite{x,y,z}. For this challenge, researchers are exploring multi-controller networks, with interacting controllers, thus bringing back distributed control planes~\cite{x,y,z} and their current programming difficulties.

In this paper, we ask if it is possible to centrally program distributed control planes.
Operators should be able to directly express network-wide policies, which are automatically decomposed into individual device configurations. The resulting forwarding behavior, which emerges through device interactions, must be policy-compliant under all possible failures.
If successful, this approach would combine easy programmability of centralized control planes and failure robustness of distributed control planes. 
%
More pragmatically, it would help many networks that, for the foreseeable future, will continue to use a distributed control plane, due to the difficulty of migrating to SDN or the inherent scalability and failure-robustness of distributed control.
